\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Adam MEDRAGH} % Candidate's name
\address{+33 7 82 13 55 94 \\ Paris, France} % Candidate's contact information
\address{amedragh@gmail.com \\ linkedin.com/in/adam-medragh}  % Candidate's email and LinkedIn

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{Passionate MSc AI Student with extensive knowledge in machine learning, AI, and cybersecurity. Seeking a Machine Learning Engineer role at TikTok BRICS, Singapore to leverage my analytical skills and hands-on experience in developing intelligent solutions that enhance platform security and foster innovation.}

\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Master of Science in IT, minor in AI \& Cybersecurity} \hfill {Sep 2021 - Now} \\
{\em INSA Centre-Val de Loire} \\
Notable Courses: Machine Learning theory, Advanced design and object programming, Web application design, Algorithm and reasoning

{\bf Exchange Program specialized in AI} \hfill {Sep. 2022 - Feb. 2023} \\
{\em University POLITEHNICA of Bucharest} \\
Notable Accomplishments: Ranked No.1 among Romanian Universities in relevant AI disciplines

\end{rSection}

%----------------------------------------------------------------------------------------
% TECHNICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{TECHNICAL SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Technical Proficiencies & Python, Java, C, Bash, SQL, Hadoop, Spark, TensorFlow, PyTorch \\
Machine Learning & Deep neural nets, Transfer/multi-task learning, Reinforcement learning \\
Platforms & Linux, AWS Services, Hadoop ecosystem including Hive \\
Data Visualization & Pandas, OpenCV \\
Tools & Git, VSCode, Docker \\
\end{tabular}\\

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{EXPERIENCE}

\textbf{Machine Learning Engineering Internship} \hfill {Mar. 2024 - Today} \\
\textit{MicroSec, Singapore}
\begin{itemize}
    \itemsep -3pt {} 
    \item Developed a ML-based cybersecurity framework addressing authentication and intrusion detection.
    \item Designed and integrated ML models for vulnerability analysis and anomaly detection into production systems.
\end{itemize}

\textbf{Deep Learning Engineering Internship} \hfill {Apr. 2023 - Aug. 2023} \\
\textit{Nuclétudes, ArianeGroup}
\begin{itemize}
    \itemsep -3pt {} 
    \item Worked on object recognition software to enhance satellite map analysis leveraging Python and deep learning frameworks.
\end{itemize}

\textbf{AI \& Machine Learning Research Activity} \hfill {Dec. 2022 - Feb. 2023} \\
\textit{University POLITEHNICA of Bucharest}
\begin{itemize}
    \itemsep -3pt {} 
    \item Collaborated on AI research to develop a conversational AI agent for social media authenticity checks.
\end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}

\begin{itemize}
    \item [\textbullet] {\bf AI Project Leader:} Developed a real-time speech synthesis tool with Python and TensorFlow as a part of a student team project.
    \item [\textbullet] {\bf French National Student Entrepreneur:} Currently holding status due to involvement in tech innovation and AI-driven entrepreneurial activities. 
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	CERTIFICATIONS AND LANGUAGES
%----------------------------------------------------------------------------------------

\begin{rSection}{CERTIFICATIONS \& LANGUAGES} 

{\bf Certifications}
\begin{itemize}
    \item Neural Networks and Deep Learning - Coursera
    \item Intro to TensorFlow for AI, ML, and Deep Learning - DeepLearning.AI
    \item What is Data Science? - IBM
\end{itemize}

{\bf Languages}
\begin{itemize}
    \item English: Native
    \item French: Native
    \item German: Conversant - B1
    \item Arabic: Basic Knowledge (Reading \& Writing)
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	LEADERSHIP & EXTRACURRICULARS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{LEADERSHIP \& EXTRACURRICULAR ACTIVITIES} 

\begin{itemize}
    \item Directed Sport division for High Five 2022, the second largest event of Bourges in 2022.
    \item Served as Treasurer for the 2021 Poker Student Club, managing funds and contributing to team development and self-awareness.
\end{itemize}

\end{rSection}

\end{document}